Growth model analysis 3spp WB

### 2019-03-06 MS_Analysis_3spp_4rivers_Patterns_from 2spp.Rmd
fix naming error

#####################################################
#####################################################
# SElect THIS for metaPop analysis, or
groupingVariables <- c('species','metaPop01','ageInSamples', 'year','season','age')
groupingVariablesNoYear <- c('species','metaPop01','ageInSamples','season','age')

# THIS for 4 river analysis
#groupingVariables <- c('species','riverOrdered','ageInSamples','year','season','age')
#groupingVariablesNoYear <- c('species','riverOrdered','ageInSamples','season','age')

@@

@@

@@

>>>>

#####################################################
#####################################################
# SElect THIS for metaPop analysis, or
#groupingVariables <- c('species','metaPop01','ageInSamples', 'year','season','age')
#groupingVariablesNoYear <- c('species','metaPop01','ageInSamples','season','age')

# THIS for 4 river analysis
groupingVariables <- c('species','riverOrdered','ageInSamples','year','season','age')
groupingVariablesNoYear <- c('species','riverOrdered','ageInSamples','season','age')

@@

############################################################################################################
#########################
#### gr here, len above

@@

ggsave(paste0('figures/meanGRsOverAge_',riverGroupVar,'.png'), width = 6, height = 6, units='in')

@@

ggsave(paste0('figures/meanGRsOverAgeBKT_',riverGroupVar,'.png'), width = 6, height = 6, units='in')
